Q1: Are lake and terrestrial primary productivity coherent?

### 2019-05-21 AnalysisCode/ms1_analyses.Rmd
ms1 analyses v1 not so good

# Data important and formatting

```{r limno import and formatting, echo=TRUE, cache=TRUE}

lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), tsvars=c("chla"), 
                                  minmos=3, minobs=3, timespan=c(1989,2018))
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)

rm(lakes_to_get)

MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
                                    infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
MNMPCAlakes.cln<-cleanAnnualts(MNMPCAlakes.raw)

WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)

analysislakes<-list(lakeinfo=rbind(lagoslakes.cln$lakeinfo,MNMPCAlakes.cln$lakeinfo,WIDNRlakes.cln$lakeinfo),
                    lakedata=c(lagoslakes.cln$lakedata, MNMPCAlakes.cln$lakedata, WIDNRlakes.cln$lakedata))

any(duplicated(analysislakes$lakeinfo$lagoslakeid)) #no duplicates

```{r AVHRR data import, echo=FALSE, cache=TRUE}

dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)

accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")

nlcdwater<-raster("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/landcover/nlcd2011_cls11.img")
watermask<-nlcdwater<0.05

accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
maxndvi<-mask(maxndvi,watermask,maskvalue=0)

analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")

@@

image(accndvi)
points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])

@@

```{r compute coherences, echo=TRUE, cache=FALSE}

@@

modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
```

@@

#short timescales
fm.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
dredge.coh.accndvi.st<-dredge(fm.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
print(dredge.coh.accndvi.st)

fm.p.accndvi.st<-gls(accndvip.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
dredge.p.accndvi.st<-dredge(fm.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
print(dredge.p.accndvi.st)

#long timescales
fm.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
dredge.coh.accndvi.lt<-dredge(fm.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
print(dredge.coh.accndvi.lt)

fm.p.accndvi.lt<-gls(accndvip.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
dredge.p.accndvi.lt<-dredge(fm.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
print(dredge.p.accndvi.lt)
```

>>>>

# Data import

Data produced in 'ms1_prep.Rmd' are loaded.

```{r load workspace, echo=TRUE, cache=FALSE}

load("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")

@@

# image(accndvi)
# points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])

@@

```{r compute coherences, echo=TRUE, cache=TRUE}

@@

modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1
```

@@

#short timescales
fm.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.coh.accndvi.st)
dredge.coh.accndvi.st<-dredge(fm.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

fm.p.accndvi.st<-gls(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.p.accndvi.st)
dredge.p.accndvi.st<-dredge(fm.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.p.accndvi.st))

fm.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.phi.accndvi.st)
dredge.phi.accndvi.st<-dredge(fm.phi.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.st))

#long timescales
fm.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.coh.accndvi.lt)
dredge.coh.accndvi.lt<-dredge(fm.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

fm.p.accndvi.lt<-gls(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.p.accndvi.lt)
dredge.p.accndvi.lt<-dredge(fm.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.p.accndvi.lt))

fm.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                       correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(fm.phi.accndvi.lt)
dredge.phi.accndvi.lt<-dredge(fm.phi.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.lt))
```
